Optimizing the Robotics Closet

### 2018-11-30 paper.tex
Fixed a couple bugs, updated paper

Another simplifying assumption we made is that all shelves have one unit of depth.
In other words, we cannot insert items one behind another. This is a valid assumption
to make because having to pull an item from behind another would drastically reduce the
retrieval time of both items, undoing much of the benefits of our optimization. This
can be adjusted to be a soft constraint (penalize heavily for items that are one
behind another) if the model is infeasible without this change. In the meantime, we
are reasonably confident that disallowing multiple units of depth is the best
approach keeping in mind our ultimate goal of convenience.

@@

Lastly, we assumed that there can be on average 3 items in the same 1-D linear
segment. We arrived at this assumption by noticing that the fast majority of
items are in the same type of box, which are 21 cm wide. Since shelf widths
range from 74 cm to 91 cm, 3 boxes fit comfortably on three shelves. This
also has the advantage of providing padding to the items to ease retrieval. 

@@

shelf $s$ is represented as an ordered triple $(d, a, c)$, where $d$ is the
distance from the door in ``shelf-lengths'', $a$ is the area of the shelf, and
$c$ is the connected components to which the self belongs.

@@

Each item is represented with an ordered triple $(a, p, s)$, where $a$ is the area

@@

subsystem. Notice that we represent each item as a 2-dimensional area. This is valid
because we assumed that each shelf had a single unit of depth. As a preprocessing step,
we choose to minimize the area. However, we cannot rotate always the item into a
horizontal orientation. Therefore, $h$ is constant. For an item $i$ with length $l_i$,
width $w_i$, and height $h_i$, its area $a_i$ is given by 
$$a_i = \min(l_i, w_i) \cdot h_i$$

@@

Let there be $n$ shelves and $m$ items, $k$ subsystems, and $l$ is the number of
connected components. Our decision variables lie in two matrices

@@

$C$ is a $l \times k$ matrix because there are l connected components and k subsystems. \\
Note about notation: $a^i_k$ indicates the area of item $k$ while $a^s_k$ indicates the
area of shelf k. $I$ is the set of items and $S$ is the set of shelves. For any item

@@

\item $\sum_{j = 1}^{m}w_{ij}a^i_j \leq w^s_i, 1 \leq i \leq n$.

@@

\textbf{Explanation of Constraints:}
\begin{enumerate}
\item The sum of all of the items on a given shelf must be less than or equal to
  the maximum area that the shelf can support. We multiply by $w_{ji}$ so that
  items not included on the shelf are not counted.
\item Each column of $W$ can only have one $1$, because we cannot put an item
  on two shelves simultaneously. Since each row represents a shelf, we simply
  traverse the whole column and ensure its sum is exactly $1$. Notice that if
  we had put $\leq 1$, the constraint would have been invalid because then
  no items would have been included. Thus, this constraint implicitly enforces
  the constraint that every item be included.
\item Each column of $C$ can only have one $1$ because all items belonging to
  a subsystem must be in the same connected component, and therefore a subsystem
  can be in exactly one connected component. Similarly to constraint 2, summing
  this and ensuring that the sum is 1 enforces the idea that every subsystem is
  included.
\item The intuition behind this constraint is that either all items belonging
  to a subsystem are in the same connected component, or none are. Thus, we
  use the decision variable $c_{ji}$ to choose whether the sum is $0$ or not.
\end{enumerate}

@@

\section{Acknowledgements}
We would like to thank:
\begin{itemize}
\item Dr. Sara Billey for providing us with guidance throughout the project,
\item Hongyu Cao for supplying us with a paper that inspired a significant portion of our thoughts on the problem,
\item Husky Robotics for providing the closet to undergo optimization,
\item Nolan Donovan for working with us to understand and solve this problem.
\end{itemize}

>>>>

We also assumed that there can be on average 3 items in the same 1-D linear
segment. This means that by using some combination of placing items behind
and above other items, we can fit 3 items in that segment. This is a rough
estimate that we came to empirically. This makes sense because some shelves are
very deep, and all shelves fit at least 2 of the boxes vertically, since
the boxes are 12.5 cm tall, and all shelves are taller than 25 cm. 

@@

The previous assumption let us assume for our model is shelves have one unit of depth
and one unit of height. In other words, the model does not have to take into account
insertion of items one behind another. To model height, we make use of the previous
assumption to ``duplicate'' shelves, defining the duplicates to be above the original
one. We can model depth in the same way. 

@@

shelf $s$ is represented as an ordered triple $(d, l, c)$, where $d$ is the
distance from the door in ``shelf-lengths'', $l$ is the length of the shelf, and
$c$ is the connected component to which the self belongs.

@@

Each item is represented with an ordered triple $(l, p, s)$, where $l$ is the length

@@

subsystem. Notice that we represent each item as a 1-dimensional length. This is valid
because we assumed that each shelf had a single unit of depth and a single
unit of height. As a preprocessing step, minimize the length. Since we cannot always
rotate an item into a horizontal orientation, for an item with dimensions $a \times b$
the item's 1-dimensional length is given by 
$$l = \min(a, b)$$

@@

Let there be $n_0$ shelves and $m$ items, $k$ subsystems, and $n_c$ be the number of
connected components. In order to simulate stacking and placing behind, we
multiply the number of shelves by our assumed average number of items per
1-dimensional block. In our model, we chose 3 as our constant. Thus,
the total number of shelves in the model is $n = 3n_0$. 
Our decision variables lie in two matrices

@@

$C$ is a $n_c \times k$ matrix because there are l connected components and k subsystems. \\
Note about notation: $l^i_k$ indicates the length of item $k$ while $l^s_k$ indicates the
length of shelf k. $I$ is the set of items and $S$ is the set of shelves. For any item

@@

\item $\sum_{j = 1}^{m}w_{ij}l^i_j \leq l^s_i, 1 \leq i \leq n$.

@@

\textbf{Explanation of Constraints:}
\begin{enumerate}
\item The sum the lengths of all of the items on a given shelf must be less than or equal to
  the maximum length that the shelf can support. We multiply by $w_{ji}$ so that
  items not included on the shelf are not counted.
\item Each column of $W$ can only have one $1$, because we cannot put an item
  on two shelves simultaneously. Since each row represents a shelf, we simply
  traverse the whole column and ensure its sum is exactly $1$. Notice that if
  we had put $\leq 1$, the constraint would have been invalid because then
  no items would have been included. Thus, this constraint implicitly enforces
  the constraint that every item be included.
\item Each column of $C$ can only have one $1$ because all items belonging to
  a subsystem must be in the same connected component, and therefore a subsystem
  can be in exactly one connected component. Similarly to constraint 2, summing
  this and ensuring that the sum is 1 enforces the idea that every subsystem is
  included.
\item The intuition behind this constraint is that either all items belonging
  to a subsystem are in the same connected component, or none are. Thus, we
  use the decision variable $c_{ji}$ to choose whether the sum is $0$ or not.
\end{enumerate}

@@

\section{Acknowledgements}
We would like to thank:
\begin{itemize}
\item Prof. Sara Billey for providing us with guidance throughout the project,
\item Hongyu Cao for supplying us with a paper that inspired a significant portion of our thoughts on the problem,
\item Husky Robotics for providing the closet to undergo optimization,
\item Nolan Donovan for working with us to understand and solve this problem.
\end{itemize}
